---
title: "Retraction Analysis Library"
format:
  html:
    code-fold: true
---

Descriptive analysis of retraction watch data, downloaded [here](https://www.crossref.org/labs/retraction-watch/).

Now located [here](https://gitlab.com/crossref/retraction-watch-data). SJR Data located [here](https://github.com/Michael-E-Rose/SCImagoJournalRankIndicators).

Explanation for the categories is [here](https://retractionwatch.com/retraction-watch-database-user-guide/retraction-watch-database-user-guide-appendix-b-reasons/)

The evidence that "withdrawal" used to be a term is [here](https://web.archive.org/web/20240520103212/https://retractionwatch.com/retraction-watch-database-user-guide/retraction-watch-database-user-guide-appendix-b-reasons/). Still present at last crawl of 2024, and absent by the [first crawl of 2025](https://web.archive.org/web/20250124120100/https://retractionwatch.com/retraction-watch-database-user-guide/retraction-watch-database-user-guide-appendix-b-reasons/).

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
# Install the local library with: devtools::install("retractionwatch")
# or load it during development with: devtools::load_all("retractionwatch")
# At the moment we are using the development version
devtools::install("retractionwatch")
devtools::load_all("retractionwatch")
# Once the package is installed, you can load it with library(retractionwatch)
# library(retractionwatch)
library(plotly)

# # Loading data

sjr_country_counts <- build_sjr_country_counts("data/sjr_rankings")
oecd_countries <- load_oecd_countries("data/oecd_countries.csv")
retraction_data <- load_retraction_data("data/retraction_watch.csv")
publication_counts <- publication_counts_by_class(sjr_country_counts, oecd_countries)

# Clean retraction data
#retraction_reason_conversion <- readr::read_csv(reason_groupings_path,
#                                                show_col_types = FALSE)
#retraction_data %>%
#  clean_retraction_data(oecd_countries, retraction_reason_conversion) %>%
#  add_country_class(oecd_countries)
```

# Top 3 retraction reasons of each year

## In the OECD

```{r}
retraction_data_oecd <- retraction_data |>
  subset(Country %in% oecd_countries$Name)
ggplotly(plot_retraction_reasons_over_time(retraction_data_oecd, year_limits = c(2000, 2026), n_top = 3))
```

## In the UK

```{r}
retraction_data_uk <- retraction_data |>
  subset(Country == "United Kingdom")
ggplotly(plot_retraction_reasons_over_time(retraction_data_uk, year_limits = c(2000, 2026), n_top = 3))
```

# New analysis: between country explanation for rates

We know that changes over time in both a) how retractions are reported, and b)
retraction watch's data processing practice for them make temporal patterns
complex to interpret. What is more robust is inter-country comparisons.

```{r}
retraction_rates <- compute_retraction_rates(retraction_data, publication_counts)
ggplotly(plot_retraction_rates(retraction_rates)) %>% 
    layout(xaxis = list(autorange = TRUE), yaxis = list(autorange = TRUE))
```

# Applying reasons: United Kingdom vs Other OECD

```{r}
reasons_compare_results <- retraction_data |>
  reason_flags("country_class") |>
  compare_reason_groups("country_class", "United Kingdom", "Other OECD")
ratios <- group_count_ratios(reasons_compare_results, "United Kingdom", "Other OECD")
reasons_compare_results <- flag_low_counts(reasons_compare_results, ratios)

ggplotly(plot_reason_counts_scatter(reasons_compare_results, ratios))
```

```{r}
sig_plot <- significant_reasons_long(reasons_compare_results,
                                     p_col = "p_adj_filtered",
                                     exclude_low_count = TRUE)
ggplotly(plot_significant_reasons(sig_plot))
```

# AI retractions by country and scenario

**TODO: plot each scenario separately by converting them to plotly objects using ggplotly() and then combining them with subplot()**

```{r}
retraction_ai_rates <- compute_ai_rates_by_country(retraction_data, sjr_country_counts)

plot_all_scenarios(retraction_ai_rates, interactive = TRUE)
```

###  AI retractions by country and scenario, filtered to countries with at least 10 retractions

**TODO: plot each scenario separately by converting them to plotly objects using ggplotly() and then combining them with subplot()**

```{r}
plot_all_scenarios(subset(retraction_ai_rates, retractions > 10),
                   x = "ai_retraction_share_pct",
                   xlab = "Fraction of all retractions that mention AI",
                   interactive = TRUE)
```

###  AI retractions by country in the OECD

```{r}
plot_all_scenarios(subset(retraction_ai_rates, Country %in% oecd_countries$Name),
                   x = "ai_retraction_share_pct",
                   xlab = "Fraction of all retractions that mention AI",
                   interactive = TRUE)
```


# Time series plot of AI retractions

```{r}
retraction_ai_counts_ts <- compute_ai_counts_ts(retraction_data)
ggplotly(plot_ai_ts(retraction_ai_counts_ts))
```

## Time series plot of AI retractions as a proportion of all retractions

```{r}
retraction_ai_prop_ts <- compute_ai_proportion_ts(retraction_data)
ggplotly(plot_ai_ts(retraction_ai_prop_ts, "prop_ai", "AI Retractions (proportion)"))
```

# Looking for interactions with is_international flag (UK only)

```{r}
reasons_compare_results_uk <- retraction_data |>
  subset(Country == "United Kingdom") |>
  reason_flags("international") |>
  compare_reason_groups("international", FALSE, TRUE)

sig_results_uk <- significant_reasons_long(reasons_compare_results_uk,
                                           group_a = FALSE, group_b = TRUE,
                                           labels = c("domestic", "international"),
                                           min_total_count = 40)
ggplotly(plot_significant_reasons(sig_results_uk))
```