---
title: "Retraction Analysis"
format:
  html:
    code-fold: true
---

```{r}

library(dplyr)
library(tibble)
library(tidyr)
library(readr)
library(lubridate)
library(ggplot2)
library(httr)
library(readxl)
library(tidyverse)
library(janitor)

files <- list.files(
  "data/sjr_rankings",
  pattern = "^scimagojr country rank .*\\.xlsx$",
  full.names = TRUE
)

sjr_country_counts <- map_dfr(files, function(f) {

  year <- str_extract(basename(f), "\\d{4}")

  read_excel(f) %>%
    mutate(Year = as.integer(year))
})

write_csv(
  sjr_country_counts,
  "data/scimagojr_country_rank_all_years.csv"
)
sjr_country_counts <- readr::read_csv("data/scimagojr_country_rank_all_years.csv")

clean_data <- function(retraction_data, 
                       oecd_countries,
                       retraction_reason_conversion,
                       long_df_by_countries=T
){
  
  
  # Cleaning reasons for retraction
  retraction_data$Reason <- gsub('+', '', retraction_data$Reason, fixed=T)
  # Remove trailing colon
  retraction_data$Reason <- gsub(';$', ';', retraction_data$Reason)
  # Unique all countries
  all_country_names <- unique(unlist(strsplit(retraction_data$Country, ';')))
  
  
  # Number of countries involved in each article
  retraction_data$number_of_countries <- lapply(retraction_data$Country, function(x){
    x <- strsplit(x, ';')
    return(length(unlist(x)))
  }) %>% unlist()
  
  # Cleaning Dates 
  retraction_data$OriginalPaperDate <- gsub(' 0:00',
                                            '', 
                                            retraction_data$OriginalPaperDate)
  retraction_data$OriginalPaperDate <- mdy(retraction_data$OriginalPaperDate)
  
  retraction_data$RetractionDate <- gsub(' 0:00',
                                         '', 
                                         retraction_data$RetractionDate)
  retraction_data$RetractionDate <- mdy(retraction_data$RetractionDate)
  
  retraction_data <- retraction_data %>% 
    mutate(retraction_year = format(RetractionDate, "%Y"),
           publication_year = format(OriginalPaperDate, "%Y"))
  
  
  grouped_reasons <- sapply(unique(retraction_reason_conversion$Group), function(x) {
    # All the items which belong to this group
    strs_to_check <- unique(retraction_reason_conversion$Reason[retraction_reason_conversion$Group == x])
    
    res <- lapply(retraction_data$Reason, function(y){
      any(unlist(strsplit(y,';')) %in% strs_to_check)
      
    })
    return(unlist(res))
  }, simplify=F) %>% tibble::as_tibble() %>% mutate_all(as.numeric)
  
  retraction_data <- bind_cols(retraction_data,grouped_reasons)
  
  retraction_data$retracted_within_year <- case_when(
    (retraction_data$RetractionDate - retraction_data$OriginalPaperDate)/365.25 <=1 ~ 'Within 1 year',
    (retraction_data$RetractionDate - retraction_data$OriginalPaperDate)/365.25 >1~ 'After 1 year')
  
  retraction_data$retracted_within_two_years <- case_when(
    (retraction_data$RetractionDate - retraction_data$OriginalPaperDate)/365.25 <=2 ~ 'Within 2 years',
    (retraction_data$RetractionDate - retraction_data$OriginalPaperDate)/365.25 >2~ 'After 2 years')
  
  
  # Reformatting Data for one 
  # country per row. Please note
  # this will mean duplicate retractions
  # for papers with more than country 
  # per paper
  
  if(long_df_by_countries==T){
    retraction_data$paper_index <- 1:nrow(retraction_data)
    retraction_data <- retraction_data %>%
      # create row ID:
      mutate(row = row_number()) %>%
      # separate rows on " /":
      separate_rows(Country, sep = ';') 
    
    retraction_data$oecd <- case_when(
      retraction_data$Country %in% oecd_countries$Name ~ 'OECD',
      TRUE ~ 'Non-OECD'
    )
    retraction_data$UK <- case_when(
      retraction_data$Country =="United Kingdom" ~ 'UK',
      TRUE ~ 'Non-UK'
    )
  }
  
  retraction_data <- retraction_data |>
    group_by(`Record ID`) |>
    mutate(international = if_any(Country, ~n_distinct(.) > 1)) %>%
    ungroup()
  
  retraction_data$Mass_Retraction <- case_when(
    retraction_data$Publisher=='IEEE: Institute of Electrical and Electronics Engineers'&
      (retraction_data$publication_year %in% c(2009,2010,2011) | retraction_data$retraction_year %in% c(2009,2010,2011)) ~ 'IEEE Mass Retraction',
    retraction_data$Publisher=='Hindawi'&
      (retraction_data$retraction_year %in% c(2022,2023,2014)) ~ 'Hindawi Mass Retraction',
    TRUE ~ 'Other')
  retraction_data$Mass_Retraction <- factor(retraction_data$Mass_Retraction,
                                            levels = c('IEEE Mass Retraction','Hindawi Mass Retraction','Other'))
  
  # retraction_data$hindawi_retr <- case_when(
  #   retraction_data$Publisher=='Hindawi'&
  #     (retraction_data$retraction_year %in% c(2022,2023,2014)) ~ 'Hindawi',
  #   TRUE ~ 'Other')
  
  retraction_data$publication_year <- as.numeric(retraction_data$publication_year)
  retraction_data$retraction_year <- as.numeric(retraction_data$retraction_year)
  retraction_data$RetractionID = retraction_data["Record ID"]
  return(retraction_data)
  
}

retraction_data <- readr::read_csv('data/retraction_watch.csv')
oecd_countries <- read_csv("data/oecd_countries.csv") %>%
  mutate( # Rename mismatches
    Name = recode(
      Name,
      "Korea" = "South Korea",
      "Slovak Republic" = "Slovakia"
    )
  )
retraction_reason_conversion <- readr::read_csv('data/retraction_reason_groupings.csv')
# reason_lookup <- read_csv("data/retraction_reason_groupings.csv") %>%
#   filter(Group != "Ungrouped") %>%
#   distinct(Reason, Group)
retraction_data <- clean_data(retraction_data, oecd_countries, retraction_reason_conversion)

head(retraction_data)
```

Setting up the country groups of interest:

```{r}
country_groups <- c(
  "United Kingdom",
  "Other OECD",
  "Rest of World"
)

retraction_data <- retraction_data %>%
  mutate(
    country_class = case_when(
      Country == "United Kingdom" ~ "United Kingdom",
      Country %in% oecd_countries$Name     ~ "Other OECD",
      TRUE                        ~ "Rest of World"
    )
  )
```

Applying the same categorisation to the matched publication rate data:

```{r}
sjr_country_counts <- sjr_country_counts %>%
  mutate(
    country_class = case_when(
      Country == "United Kingdom" ~ "United Kingdom",
      Country %in% oecd_countries$Name     ~ "Other OECD",
      TRUE                        ~ "Rest of World"
    )
  )

publication_counts <- sjr_country_counts %>%
  group_by(
    publication_year = Year,
    country_class
  ) %>%
  summarise(
    total_papers = sum(Documents, na.rm = TRUE),
    .groups = "drop"
  )
```

# New analysis: between country explanation for rates

We know that changes over time in both a) how retractions are reported, and b) retraction watch's data processing practice for them make temporal patterns complex to interpret. What is more robust is inter-country comparisons.

```{r}
scenarios <- tribble(
  ~scenario,             ~exclude_mass, ~domestic_only,
  "Raw",                 FALSE,         FALSE,
  "No mass retractions", TRUE,          FALSE,
  "Domestic only",       FALSE,         TRUE,
  "Domestic + no mass",  TRUE,          TRUE
)

retraction_counts <-retraction_data %>%
  distinct(RetractionID, .keep_all = TRUE) %>%
  mutate(
    country_class = case_when(
      Country == "United Kingdom" ~ "United Kingdom",
      Country %in% oecd_countries$Name     ~ "Other OECD",
      TRUE                        ~ "Rest of World"
    )
  ) %>%
  crossing(scenarios) %>%
  filter(
    !exclude_mass | Mass_Retraction == "Other",
    !domestic_only | !international
  ) %>%
  count(
    publication_year,
    country_class,
    scenario,
    name = "retractions"
  ) %>% na.omit
```

```{r}
retraction_rates <- retraction_counts %>%
  left_join(
    publication_counts,
    by = c("publication_year", "country_class")
  ) %>%
  mutate(
    retraction_rate = retractions / total_papers,
    retraction_rate_per_100k = 100000 * retraction_rate
  )
```

```{r}
p <- ggplot(
  retraction_rates,
  aes(
    publication_year,
    retraction_rate_per_100k,
    colour = country_class
  )
) +
  geom_line() +
  facet_wrap(~scenario, ncol = 2) +
  scale_x_continuous(
    limits = c(2000, 2023),
    breaks = seq(2000, 2023, by = 5)
  ) +
#  scale_y_log10(
#  scale_y_continuous(
#    limits = c(4, 600)
#  ) +
  labs(
    y = "Country class retraction fraction, log10-scaling",
    x = "Year",
    colour = NULL
  ) +
  #scale_y_continuous(trans='log10') +
  theme_bw()
p
```
```{r}
library(plotly)

ggplotly(p) %>%
  layout(xaxis = list(autorange = TRUE), yaxis = list(autorange = TRUE))
```

## Applying reasons

```{r}
reasons_long <- retraction_data %>%
  filter(Mass_Retraction=="Other") %>%
  select(RetractionID, publication_year, country_class, Reason) %>%
  separate_rows(Reason, sep = ";") %>%
  mutate(
    Reason = str_trim(Reason)
  ) %>%
  na.omit
  ## %>%
  #filter(!Reason =="") %>%
  ## left_join(retraction_reason_keep, by = "Reason")

reason_flags <- reasons_long %>%
  mutate(value = TRUE) %>%
  distinct(RetractionID, publication_year, Reason, .keep_all = TRUE) %>%
  pivot_wider(
    id_cols = c(RetractionID, publication_year, country_class),
    names_from = Reason,
    values_from = value,
    values_fill = FALSE,
    names_prefix = "is_"
  ) %>%
  clean_names() %>%
  mutate(
    period = if_else(
      publication_year < 2017,
      "Pre-2017",
      "Post-2017"
    )
  )
```

```{r}
reason_summary <- reason_flags %>%
  group_by(period,country_class) %>%
  summarise(
    across(
      starts_with("is_"),
      list(
        proportion = ~mean(.x, na.rm = TRUE),
        count = ~sum(.x, na.rm = TRUE)
      )
    )
  )
```

```{r}
reasons_compare_long <- reason_summary %>%
  ungroup() %>%
  pivot_longer(
    -c(period, country_class),
    names_to = c("flag", ".value"),
    names_pattern = "(is_.*)_(proportion|count)"
  )
reasons_compare_wide <- reasons_compare_long %>%
  select(period, country_class, flag, proportion, count) %>%
  pivot_wider(
    names_from = country_class,
    values_from = c(proportion, count)
  )
```

```{r}
plot(reasons_compare_wide$`count_Other OECD`,
     reasons_compare_wide$`count_United Kingdom`
     )
```
```{r}
plot_ly(data = retraction_rates, x = reasons_compare_wide$`count_Other OECD`,
     y = reasons_compare_wide$`count_United Kingdom`
     )
```


```{r}
group_sizes <- reason_flags %>%
  count(period, country_class, name = "n")

reasons_compare_results <- reasons_compare_wide %>%
  left_join(
    group_sizes %>%
      pivot_wider(
        names_from = country_class,
        values_from = n
      ),
    by = "period"
  ) %>%
  rowwise() %>%
  mutate(
    diff = `proportion_United Kingdom` - `proportion_Other OECD`,
    p_value = prop.test(
      x = c(`count_United Kingdom`, `count_Other OECD`),
      n = c(`United Kingdom`, `Other OECD`)
    )$p.value
  ) %>%
  mutate(
    across(starts_with("p.value"), ~coalesce(.x, 0))
  ) %>%
  ungroup() %>%
  mutate(
    p_adj = p.adjust(p_value, method = "BH")
  ) %>%
  arrange(desc(abs(diff)))
```

```{r}
results_lm_pre = lm(`count_United Kingdom` ~ `count_Other OECD` - 1, 
    data = reasons_compare_results %>% filter(period=="Pre-2017"))
results_lm_post = lm(`count_United Kingdom` ~ `count_Other OECD` - 1, 
    data = reasons_compare_results %>% filter(period=="Post-2017"))
ukoecd_ratio_pre=as.numeric(1/results_lm_pre$coefficients)
ukoecd_ratio_post=as.numeric(1/results_lm_post$coefficients)
```

```{r}
reasons_compare_results<- reasons_compare_results %>%
  mutate(
    significant = p_adj < 0.05,
    low_count = ifelse(period=="Pre-2017",
        ukoecd_ratio_pre*`count_United Kingdom` + `count_Other OECD` <500,
        ukoecd_ratio_post*`count_United Kingdom` + `count_Other OECD` <500)
#      pmin(`count_United Kingdom`,
#           `count_Other OECD`) < 10
  ) %>% 
  mutate(
    p_adj_filtered = NA_real_,
    p_adj_filtered = replace(
      p_adj_filtered,
      !low_count,
      p.adjust(p_value[!low_count], method = "BH")
    )
  ) %>%
  mutate(significant_filtered = p_adj_filtered < 0.05)
```

```{r}
plot_df <- reasons_compare_results %>%
  mutate(
    sig_class = case_when(
      p_adj_filtered < 0.05 & !low_count ~ "Significant (adequate count)",
      p_adj < 0.05 & low_count  ~ "Significant (low count)",
      TRUE                      ~ "Not significant"
    )
  )
boundary <- tibble(
  x = c(0, 500),
  y = (500 - x) / ukoecd_ratio_pre
) %>%
  filter(y >= 0)
meanpred_pre <- tibble(
  x = c(0, max(plot_df$`count_Other OECD`)),
  y = (x) / ukoecd_ratio_pre
)
meanpred_post <- tibble(
  x = c(0, max(plot_df$`count_Other OECD`)),
  y = (x) / ukoecd_ratio_post
)
labels <- bind_rows(
  meanpred_pre %>% slice_tail(n = 1) %>% mutate(label = "Pre-2017"),
  meanpred_post %>% slice_tail(n = 1) %>% mutate(label = "Post-2017")
)

p <- plot_df %>%
  ggplot(
    aes(
      x = `count_Other OECD`,
      y = `count_United Kingdom`,
      colour = sig_class,
      shape = period
    )
  ) +
  geom_line(
    data = boundary,
    aes(x = x, y = y),
    inherit.aes = FALSE,
    linetype = "dashed"
  ) + 
  geom_line(
    data = meanpred_pre,
    aes(x = x, y = y),
    inherit.aes = FALSE
  ) +
  geom_line(
    data = meanpred_post,
    aes(x = x, y = y),
    inherit.aes = FALSE
  ) +
  geom_text(
    data = labels,
    inherit.aes = FALSE,
    aes(x = x, y = y, label = label),
    hjust = 1,
    vjust = -1
  ) + 
  geom_point(alpha = 0.7) +
  scale_colour_manual(
    values = c("grey70", "red", "orange")
  ) +
  labs(
    x = "Count (Other OECD)",
    y = "Count (United Kingdom)",
    colour = "FDR < 0.05"
  ) +
  coord_cartesian(
    xlim = c(0, NA),
    ylim = c(0, NA)
  ) +
  theme_minimal()

ggplotly(p)  %>%
  layout(xaxis = list(autorange = TRUE), yaxis = list(autorange = TRUE))
```

```{r}
library(tidytext)

sig_results <- reasons_compare_results %>%
  filter(!is.na(p_adj), p_adj_filtered < 0.05) %>%
  filter(!low_count) %>%
  select(
    flag,
    period,
    proportion_united_kingdom = `proportion_United Kingdom`,
    proportion_other_oecd = `proportion_Other OECD`,
    diff
  )

sig_plot <- sig_results %>%
  mutate(
    flag = reorder_within(flag, abs(diff), period)
  ) %>%
  select(
    period,
    flag,
    proportion_other_oecd,
    proportion_united_kingdom
  ) %>%
  pivot_longer(
    starts_with("proportion"),
    names_to = "group",
    values_to = "proportion"
  )

```

```{r}
p <- ggplot(sig_plot,
       aes(proportion, flag)) +
  geom_line(
    aes(group = interaction(period, flag)),
    colour = "grey80"
  ) +
  geom_point(aes(colour = group),
             size = 3) +
  facet_grid(
    period ~ .,
    scales = "free_y",
    space = "free_y"
  ) +
  tidytext::scale_y_reordered()
p
```
```{r}
ggplotly(p)
```
## AI retractions by country and scenario

```{r}
publication_counts_bycountry <- sjr_country_counts %>%
  group_by(
    Country
  ) %>%
  summarise(
    total_papers = sum(Documents, na.rm = TRUE),
    .groups = "drop"
  )

retraction_counts <-retraction_data %>%
  distinct(RetractionID, .keep_all = TRUE) %>%
    crossing(scenarios) %>%
  filter(
    !exclude_mass | Mass_Retraction == "Other",
    !domestic_only | !international
  ) %>%
  count(
#    publication_year,
    Country,
    scenario,
    name = "retractions"
  )

retraction_ai_counts <-retraction_data %>%
  filter(str_detect(
    Reason,
    "Computer-Aided Content|Computer-Generated Content"
  )) %>%
  distinct(RetractionID, .keep_all = TRUE) %>%
    crossing(scenarios) %>%
  filter(
    !exclude_mass | Mass_Retraction == "Other",
    !domestic_only | !international
  ) %>%
  count(
#    publication_year,
    Country,
    scenario,
    name = "ai_retractions"
  )
retraction_ai_rates <- retraction_ai_counts %>%
  left_join(
    retraction_counts,
    by = c("Country", "scenario")
  ) %>%
  left_join(
    publication_counts_bycountry,
    by = "Country"
  ) %>%
  mutate(
    ai_retraction_share = ai_retractions / retractions,
    ai_retraction_share_pct = 100 * ai_retraction_share,
    ai_retraction_rate = ai_retractions / total_papers,
    ai_retraction_rate_per_100k = 100000 * ai_retraction_rate
  )
```

```{r}
library(dplyr)
library(ggplot2)
library(forcats)

plot_scenario <- function(dat, scenario_name,
                          x="ai_retraction_rate_per_100k",
                          xlab="AI Retractions per 100,000 papers (log scale)") {

  plot_dat <- dat %>% #na.omit %>%
    filter(scenario == scenario_name) %>%
    arrange(.data[[x]]) %>%
    mutate(
      Country = factor(Country, levels = Country)
    )

  uk_dat <- plot_dat %>%
    filter(Country == "United Kingdom")

  non_uk_dat <- plot_dat %>%
    filter(Country != "United Kingdom")

  p <- ggplot(plot_dat,
         aes(x = .data[[x]]+0.01, y = Country)) +
    geom_point(colour = "grey50", alpha = 0.6) +
    
    geom_point(
      data = uk_dat,
      colour = "red",
      size = 3
    ) +
    geom_text(
      data = non_uk_dat,
      aes(label = Country),
      colour = "grey",
      hjust = -0.1
    ) +

    geom_text(
      data = uk_dat,
      aes(label = Country),
      colour = "red",
      hjust = -0.1,
      fontface = "bold"
    ) +
    scale_x_log10(
      expand = expansion(mult = c(0.02, 0.2))
    )+

    labs(
      title = scenario_name,
      x = xlab,
      y = NULL
    ) +

    theme_minimal() +
    theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank()
    )
  return(p)
}

```

```{r}
for (s in unique(retraction_ai_rates$scenario)) {
  p <- plot_scenario(retraction_ai_rates, s)
  print(ggplotly(p))
}
```

```{r}
for (s in unique(retraction_ai_rates$scenario)) {
  tmp= retraction_ai_rates %>% filter (retractions>10)
  p <- plot_scenario(tmp, s,
                      "ai_retraction_share_pct",
                      "Fraction of all retractions that mention AI")
  print(ggplotly(p))
}
```

## Time series plot of AI retractions

```{r}
retraction_ai_counts_ts <-retraction_data %>%
  filter(str_detect(
    Reason,
    "Computer-Aided Content|Computer-Generated Content"
  )) %>%
  distinct(RetractionID, .keep_all = TRUE) %>%
    crossing(scenarios) %>%
  filter(
    !exclude_mass | Mass_Retraction == "Other",
    !domestic_only | !international
  ) %>%
  count(
    publication_year,
    country_class,
    scenario,
    name = "ai_retractions"
  )
```

```{r}
p <- ggplot(
  retraction_ai_counts_ts,
  aes(
    publication_year,
    ai_retractions,
    colour = country_class
  )
) +
  geom_point() +
  facet_wrap(~scenario, ncol = 2) +
  scale_x_continuous(
    limits = c(2000, 2025),
    breaks = seq(2000, 2025, by = 5)
  ) +
  scale_y_log10() +
  labs(
    y = "AI Retractions (counts)",
    x = "Year",
    colour = NULL
  ) +
  theme_bw()

ggplotly(p) %>%
  layout(xaxis = list(autorange = TRUE), yaxis = list(autorange = TRUE))
```

```{r}
# Denominator: all retractions
total_counts <- retraction_data %>%
  distinct(RetractionID, .keep_all = TRUE) %>%
  crossing(scenarios) %>%
  filter(
    !exclude_mass | Mass_Retraction == "Other",
    !domestic_only | !international
  ) %>%
  count(
    publication_year,
    country_class,
    scenario,
    name = "total_retractions"
  )

# Proportion
retraction_ai_prop_ts <- retraction_ai_counts_ts %>%
  left_join(
    total_counts,
    by = c("publication_year", "country_class", "scenario")
  ) %>%
  mutate(
    prop_ai = ai_retractions / total_retractions
  )
```

```{r}
p <- ggplot(
  retraction_ai_prop_ts,
  aes(
    publication_year,
    prop_ai,
    colour = country_class
  )
) +
  geom_point() +
  facet_wrap(~scenario, ncol = 2) +
  scale_x_continuous(
    limits = c(2000, 2025),
    breaks = seq(2000, 2025, by = 5)
  ) +
  scale_y_log10() +
  labs(
    y = "AI Retractions (proportion)",
    x = "Year",
    colour = NULL
  ) +
  theme_bw()
 
ggplotly(p) %>%
  layout(xaxis = list(autorange = TRUE), yaxis = list(autorange = TRUE))
```

## Looking for interactions with is_international flag

```{r}
reasons_long_uk <- retraction_data %>%
  filter(Mass_Retraction=="Other",
         Country == "United Kingdom") %>%
  select(RetractionID, publication_year, international, Reason) %>%
  separate_rows(Reason, sep = ";") %>%
  mutate(
    Reason = str_trim(Reason)
  ) %>%
  na.omit
  ## %>%
  #filter(!Reason =="") %>%
  ## left_join(retraction_reason_keep, by = "Reason")

reason_flags_uk <- reasons_long_uk %>%
  mutate(value = TRUE) %>%
  distinct(RetractionID, publication_year, Reason, .keep_all = TRUE) %>%
  pivot_wider(
    id_cols = c(RetractionID, publication_year, international),
    names_from = Reason,
    values_from = value,
    values_fill = FALSE,
    names_prefix = "is_"
  ) %>%
  clean_names() %>%
  mutate(
    period = if_else(
      publication_year < 2017,
      "Pre-2017",
      "Post-2017"
    )
  )

reason_summary_uk <- reason_flags_uk %>%
  group_by(period,international) %>%
  summarise(
    across(
      starts_with("is_"),
      list(
        proportion = ~mean(.x, na.rm = TRUE),
        count = ~sum(.x, na.rm = TRUE)
      )
    )
  )
```

```{r}
reasons_compare_long_uk <- reason_summary_uk %>%
  ungroup() %>%
  pivot_longer(
    -c(period, international),
    names_to = c("flag", ".value"),
    names_pattern = "(is_.*)_(proportion|count)"
  )
reasons_compare_wide_uk <- reasons_compare_long_uk %>%
  select(period, international, flag, proportion, count) %>%
  pivot_wider(
    names_from = international,
    values_from = c(proportion, count)
  )
```

```{r}
group_sizes_uk <- reason_flags_uk %>%
  count(period, international, name = "n")

reasons_compare_results_uk <- reasons_compare_wide_uk %>%
  left_join(
    group_sizes_uk %>%
      pivot_wider(
        names_from = international,
        values_from = n
      ),
    by = "period"
  ) %>%
  rowwise() %>%
  mutate(
    diff = `proportion_FALSE` - `proportion_TRUE`,
    p_value = prop.test(
      x = c(`count_FALSE`, `count_TRUE`),
      n = c(`FALSE`, `TRUE`)
    )$p.value
  ) %>%
  mutate(
    across(starts_with("p.value"), ~coalesce(.x, 0))
  ) %>%
  ungroup() %>%
  mutate(
    p_adj = p.adjust(p_value, method = "BH")
  ) %>%
  arrange(desc(abs(diff)))
```

### Plot it

```{r}

sig_results_uk <- reasons_compare_results_uk %>%
  filter(!is.na(p_adj), p_adj < 0.05,
         count_FALSE + count_TRUE > 40 ) %>%
  mutate(
    flag = reorder_within(flag, abs(diff), period)
  ) %>%
  rename(
  domestic = proportion_FALSE,
  international = proportion_TRUE
  ) %>%
  select(
    period,
    flag,
    domestic,
    international
  ) %>%
  pivot_longer(
    c(domestic, international),
    names_to = "group",
    values_to = "proportion"
  )
```

```{r}
p <- ggplot(sig_results_uk,
       aes(proportion, flag)) +
  geom_line(
    aes(group = interaction(period, flag)),
    colour = "grey80"
  ) +
  geom_point(aes(colour = group),
             size = 3) +
  facet_grid(
    period ~ .,
    scales = "free_y",
    space = "free_y"
  ) +
  tidytext::scale_y_reordered()

ggplotly(p)  %>%
  layout(xaxis = list(autorange = TRUE), yaxis = list(autorange = TRUE))
```
